\documentclass[margin,line]{resume}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{pifont}



\hypersetup{colorlinks=true, urlcolor=blue}

%\renewcommand{\familydefault}{\sfdefault}
%\renewcommand{\sfdefault}{iwona}

\begin{document}
\name{\LARGE{\textsc{Niladri Das}}}
\begin{resume}

    %__________________________________________________________________________________________________________________
	% Contact Information
    \section{\mysidestyle Contact\\Information}

    Aerobotics Lab, \#201, Reed-McDonald Bldg,   		\hfill E-Mail : \href{mailto:niladridas@tamu.edu}{\texttt{niladridas@tamu.edu}} \\
	Dept. of Aerospace Engineering, Texas A\&M,                   \hfill \hfill GitHub : \href{https://github.com/niladridas}{\texttt{github.com/niladridas}} \\
	 575 Ross St, College Station, TX 77843

    \section{\mysidestyle Current\\Position}
    Ph.D. candidate working on development and application of methodologies in the broad area of uncertainty quantification and filtering.
%    \begin{itemize}[topsep=2pt, partopsep=1pt, itemsep=2pt, parsep=1pt, leftmargin=15pt]
%\item{Mathematical Control Theory}  \item{Robotics} \item{Machine Learning}
%\subitem{Learning Through Demonstration}
%\subitem{Probabilistic Models and Dynamical Systems}
%\subitem{Vision}

%\end{itemize}

    %__________________________________________________________________________________________________________________
    % Education
    \section{\mysidestyle Education}
    Doctor of Philosophy in Aerospace Engineering \hfill Adviser: Dr. R. Bhattacharya\\
    Texas A\&M University, USA \hfill 2015 - Present \\
    \textbf{Dissertation}: Developing new Space Situational Awareness \hfill GPA: 3.826/4\\algorithms for improved real-time tracking of space objects.

    \vspace{-2mm}

	Master of Technology in Electrical Engineering \hfill Adviser: Dr. L. Behera\\
	Indian Institute of Technology Kanpur, India\hfill 2012 - 2014\\
	\textbf{Dissertation}: Learning to Grasp \& Programming by \hfill GPA : 7.91/10 \\Demonstration
	Using a 7-DOF Barrett Arm.

\vspace{-2mm}

	Bachelor of Engineering in Electrical Engineering \hfill Adviser: Dr. A. Chatterjee \\
	Jadavpur University, Kolkata, India \hfill  2008 - 2012 \\
	\textbf{Project}: Image Processing Based Object Detection.\hfill GPA : 7.84/10

\section{\mysidestyle Experiences}

    \emph{Graduate Assistant  Researcher}\hfill Adviser: Dr. R. Bhattacharya\\
    Dept. of Aerospace Engineering, Texas A\&M.\hfill Sep 2015-Present\\
    Working on an Air Force Project about Space Situational Awareness. \\It involves collaborating with Dept. of Statistics of TAMU, \\developing and implementing particle based non-linear filters.

    \emph{Project Associate}\hfill Adviser: Dr. L. Behera\\
    Dept. of Electrical Engineering, IIT Kanpur\hfill Jan 2015 - Jun 2015\\
    Worked on a project to implement Non-linear control technique\\ (Higher Order Sliding Mode Control) on 7 degree of freedom \\Barrett WAM. Developed physics based Inverse Dynamic Model.\\ Developed Gaussian Mixture based model to compensate the unknown \\non-linearities. This work led to a conference publication.

    \emph{Project Associate}\hfill Adviser: Dr. L. Behera\\
    Dept. of Electrical Engineering, IIT Kanpur\hfill Aug 2014 - Jan 2015\\
    Worked on a project to develop dynamical system based trajectory \\learning for a 7 DoF robot arm. Implemented Gaussian Mixture \\based model to learn trajectories from Kinesthetic teaching. \\Developed a method to relax the restriction of unique attractor point \\during training. This work lead to a conference publication.


    \emph{Graduate Research Experience}\hfill Adviser: Dr. L. Behera\\
    Dept. of Electrical Engineering, IIT Kanpur\hfill July 2013-July 2014\\
    Worked on the Masters Thesis. This work involved solving inverse \\kinematic problem for a 7 DoF Redundant Manipulator, implementing \\Kinect based Object segmentation for grasping using Deep Learning, \\developing a hand-eye autonomous calibration technique and eventually\\ implementing Symbolic Encoding based skill learning. \\This thesis led to a conference publication.

   \emph{Graduate Teaching Assistant} \hfill Supervisor: Dr L. Behera\\
   Dept. of Electrical Engineering, IIT Kanpur \hfill Jan 2014 - May 2014\\
   Course: Basics of Modern Control System. \hfill Aug 2013 - Nov 2013\\
   Checking assignments and teaching Matlab to solve control systems\\ related problems

    \emph{Graduate Teaching Assistant} \hfill Supervisor: Dr. R. Potluri\\
   Dept. of Electrical Engineering, IIT Kanpur \hfill Jan 2013 - Apr 2013\\
   Course: Basics of Modern Control System. \\
   Checking assignments and teaching Octave to solve control systems\\ related problems


    \vspace{-2mm}
%    \emph{Graduate Course Project}\hfill Adviser: Dr. N. Naik\\
%    Dept. of Electrical Engineering, IIT Kanpur\hfill May 2013 - Jun 2013\\
%    Course: Computational aspect of Tomographic Imaging.\\
%    Project: Solving Nonogram Using Heuristics.\\
%    Implemented a heurtic optimization algorithm (ABC) to solve \\nonograms, a form of tomographic image. Nonograms are a very \\popular form of puzzle in Japan and are known as Hanji.



%	\vspace{-2mm}

%	\emph{Under Graduate Research}\hfill Dr. A. Chatterjee\\
%	Department of Electrical Engineering, Jadavpur University\\
%	Project: Image Processing Based Object Detection\\
%	Implemented vision based feature extraction technique(SIFT) to \\identify an object
%	These feature were used for navigating a robot.

%	\vspace{-2mm}

%	\emph{Undergraduate Projects}\\
%    Dept. of Electrical Engineering, Jadavpur University

%    \begin{itemize}
%    \item Hardware Design and Software simulation of Sallen-Key \hfill Adviser: Prof. B. Bhattacharyya \\ Low Pass Filter.
%    \item Software Implementation of Voltage Controlled Oscillator \hfill Adviser: Prof. B. Bhattacharyya
%    \item Neural Compensation of Vector-Voltmeter \hfill Adviser: Dr. A Chatterjee
%    \item GUI application in Visual Basic(VB) for a Data Acquisition \hfill Adviser: Dr. A. Chatterjee\\System
%    \end{itemize}
%	\vspace{-2mm}


    \emph{Student Mentoring}\\
    Dept. of Electrical Engineering, IIT Kanpur\\
    Intelligent Systems Laboratory

    \begin{itemize}
    \item As a Project Assistant supervised a Masters student for his thesis
    \item As a Project Assistant taught two Masters student how to use Robot \\Operating System
    \item As a Master student mentored two Under-Graduate intern. \\They worked on implementing Deep Learning, learned how to use \\Point Cloud Library and Barrett WAM programming.
    \end{itemize}


	%

      %

      \section{\mysidestyle Publications }
      \emph{Conference}
      \begin{itemize}
        \item ``Sparse Sensing Architecture For Kalman Filtering With
Guaranteed Error Bound.''\\2017 1st IAA Conference on Space Situational Awareness, Orlando, Florida.
        \item ``Control of a 4 DoF Barrett WAM Robot - Modeling, Control Synthesis and Experimental Validation."\\2016 IEEE First International Conference on Control, Measurement and Instrumentation
        \item ``Learning Object Manipulation from Demonstration through Vision for the 7-DOF Barrett WAM."\\2016 IEEE First International Conference on Control, Measurement and Instrumentation
        \item ``A probabilistic framework of learning movement primitives from unstructured demonstrations."\\2015 IEEE 13th International Conference on Industrial Informatics
        \item ``Robot Learns from Human Teacher Through Modified Kinesthetic Teaching."\\2014 International conference on Advances in Control and Optimization of Dynamic Systems
      \end{itemize}
      \emph{Journal}
      \begin{itemize}
          \item ``Optimal Transport Based Tracking of Space Objects in Cylindrical Manifolds''. Journal of Astronautical Sciences (Springer) [\textbf{under review}]
      \end{itemize}




     %



	%

	\section{\mysidestyle Achievements}
\begin{itemize}[topsep=2pt, partopsep=1pt, itemsep=2pt, parsep=1pt, leftmargin=15pt]
    \item Ranked $\textbf{218}^{th}$(top \textbf{0.1}\%) in India in \textbf{Graduate Aptitude Test in Engineering-2012}, the national level entrance test for post-graduate studies at the Indian Institute of Technology \& {Indian Institute of Science}.
    \item Ranked $\textbf{162}^{nd}$ (top \textbf{0.1}\%) in state in \textbf{WBJEE-2008}, a state level entrance test for under-graduate studies.
    \item Recipient of Scholarship under \textit{Scheme of Scholarship for College and University Students of Govt. of India}  for State Board Examination performance ($\textbf{120}^{th}$ in Merit List).
	\end{itemize}
   % Courses Taken
 %   \section{\mysidestyle Relevant\\Courses}
 %   \emph{Graduate}
%	\begin{itemize}[topsep=2pt, partopsep=1pt, itemsep=2pt, parsep=1pt, leftmargin=15pt]
%	\item Intelligent Control Systems %(EE698B)
%	\item Computational aspect of Tomographic Imaging : Models to Inversion %(EE659)
%	\item Mathematical Structures of Signals and Systems %(EE600)
%	\end{itemize}
%
%\vspace{-2mm}
%
%	\emph{Undergraduate}
%	\item Signals \& Systems
%	\item Control System Engineering
%	\item Digital Signal Processing
%	\item Advanced Instumentation-I \& II
%	\end{itemize}

	%

	 %


    \section{\mysidestyle Skills}

	\emph{Programming Languages}\\ C , C++ , Python, Julia

	\vspace{-2mm}

    \vspace{-2mm}
	\emph{Softwares Packages}\\
	Matlab, \LaTeX, Robot Operating System, OpenCV, PCL, Eigen, Boost, OMPL.

     %
    \section{\mysidestyle Organisations}
    \begin{itemize}
        \item AIAA: \emph{The American Institute of Aeronautics and Astronautics}\\
        Student Member
        \item IEEE: \emph{Institute of Electrical and Electronics Engineers}\\
        Student Member of:
        \begin{itemize}
            \item IEEE Control System Society
            \item IEEE Aerospace and Electronic Systems Society
            \item IEEE Young Professionals
        \end{itemize}
        \item SIAM: \emph{Society for Industrial and Applied Mathematics}\\
        Graduate Student Member of:
            \begin{itemize}
                \item  SIAG on Control \& Systems Theory Member
                \item SIAG on Uncertainty Quantification Member
            \end{itemize}
        \item AGSC: \emph{Aerospace Graduate Student Council}
        \begin{itemize}
            \item Student Council Member of Aerospace Engineering Department at Texas A\&M University
            \item GPSC: Graduate and Professional Student Council delegate of Aerospace Department.
        \end{itemize}
    \end{itemize}
    \section{\mysidestyle Referees}
    \begin{itemize}
        \item Raktim Bhattacharya (Ph.D. Advisor)\\
        Associate  Professor, Departement of Aerospace Engineering\\
        Texas A\&M University \\
        Office: HRBB 727C\\
        Phone: 979.862.2914\\
        Email: raktim@tamu.edu
        \item Laxmidhar Behera (Masters Advisor)\\
        Professor, Departement of Electrical Engineering\\
        Indian Institute of Technology Kanpur\\
        Phone: +91.0512.259.7198\\
        Email : lbehera@iitk.ac.in
        \item Amitava Chatterjee (Bachelors Advisor)\\
        Professor, Departement of Electrical Engineering\\
        Jadavpur Univsersity\\
        Phone:   +91 33 2414 6949 (O), +919433960972 (Mobile)\\
        Email: achatterjee@ee.jdvu.ac.in; cha\_ami@yahoo.co.in
        \item Naren Naik \\
        Associate Professor, Department of Electrical Engineering\\
        Indian Institute of Technology Kanpur, India\\
        Office: 303A ACES, Dept. of Elec. Eng.\\
        Phone: +91 512 259 6518 \\
        Email: nnaik@iitk.ac.in
        \item Swagata Munshi (Jadavpur University)\\
        Professor, Department of Electrical Engineering\\
        Jadavpur University, Kolkata, India\\
        Phone: +91 033 2414 6949 (O)\\
        Email: smunshi@ee.jdvu.ac.in, sugatamunshi@yahoo.com
    \end{itemize}

\end{resume}
\end{document}
